Information Aggregation in Exponential Family Markets

### 2014-02-12 WriteUp/maxentpredmkts.tex
changed the title!

\begin{document}
% Page heads
\markboth{Abernethy et al.}{Maximum Entropy Prediction Markets}
% Title portion
\title{Exponential Family Markets for Information Aggregation}
\author{JACOB ABERNETHY
\affil{University of Michigan, Ann Arbor}
SINDHU KUTTY
\affil{University of Michigan, Ann Arbor}
S\'{E}BASTIEN LAHAIE
\affil{Microsoft Research, New York City}
RAHUL SAMI
\affil{Google India}}
%%\author{GANG ZHOU
%%\affil{College of William and Mary}
%%YAFENG WU
%%\affil{University of Virginia}
%%TING YAN
%%\affil{Eaton Innovation Center}
%%TIAN HE
%%\affil{University of Minnesota}
%%CHENGDU HUANG
%%\affil{Google}
%%JOHN A. STANKOVIC
%%\affil{University of Virginia}
%%TAREK F. ABDELZAHER
%%\affil{University of Illinois at Urbana-Champaign}}
% NOTE! Affiliations placed here should be for the institution where the
%       BULK of the research was done. If the author has gone to a new
%       institution, before publication, the (above) affiliation should NOT be changed.
%       The authors 'current' address may be given in the "Author's addresses:" block (below).
%       So for example, Mr. Abdelzaher, the bulk of the research was done at UIUC, and he is
%       currently affiliated with NASA.

@@

\acmformat{Jacob Abernethy, Sindhu Kutty, S\'{e}bastien Lahaie, and Rahul Sami, 2014. Maximum Entropy Prediction Markets}
%%Gang Zhou, Yafeng Wu, Ting Yan, Tian He, Chengdu Huang, John A. Stankovic, and Tarek F. Abdelzaher, 2010. A multifrequency MAC specially designed for  wireless sensor network applications.

>>>>

\begin{document}
% Page heads
\markboth{Abernethy et al.}{Information Aggregation in Exponential Family Markets}
% Title portion
\title{Information Aggregation in Exponential Family Markets}
\author{JACOB ABERNETHY
\affil{University of Michigan, Ann Arbor}
SINDHU KUTTY
\affil{University of Michigan, Ann Arbor}
S\'{E}BASTIEN LAHAIE
\affil{Microsoft Research, New York City}
RAHUL SAMI
\affil{Google India}}
%%\author{GANG ZHOU
%%\affil{College of William and Mary}
%%YAFENG WU
%%\affil{University of Virginia}
%%TING YAN
%%\affil{Eaton Innovation Center}
%%TIAN HE
%%\affil{University of Minnesota}
%%CHENGDU HUANG
%%\affil{Google}
%%JOHN A. STANKOVIC
%%\affil{University of Virginia}
%%TAREK F. ABDELZAHER
%%\affil{University of Illinois at Urbana-Champaign}}
% NOTE! Affiliations placed here should be for the institution where the
%       BULK of the research was done. If the author has gone to a new
%       institution, before publication, the (above) affiliation should NOT be changed.
%       The authors 'current' address may be given in the "Author's addresses:" block (below).
%       So for example, Mr. Abdelzaher, the bulk of the research was done at UIUC, and he is
%       currently affiliated with NASA.

@@

%\acmformat{Jacob Abernethy, Sindhu Kutty, S\'{e}bastien Lahaie, and Rahul Sami, 2014. Information Aggregation in Exponential Family Markets}
%%Gang Zhou, Yafeng Wu, Ting Yan, Tian He, Chengdu Huang, John A. Stankovic, and Tarek F. Abdelzaher, 2010. A multifrequency MAC specially designed for  wireless sensor network applications.
